Three 40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-30 papers/ms.tex
update ms

%
% Symbols
%
\newcommand{\kms}{\,km\,s$^{-1}$}
\newcommand{\mkms}{\,km\,s^{-1}}  % math mode
\newcommand{\ms}{\,m\,s$^{-1}$}
\newcommand{\bpmrpo}{(G_{\rm BP}-G_{\rm RP})_0}
\newcommand{\bpmrp}{G_{\rm BP}-G_{\rm RP}}

@@

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar group memberships
\citep[{\it e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
Broadly speaking these analyses cluster on the stellar positions and
on-sky velocities measured by Gaia, with varying degrees of filtering
and supervision.  One important result is the identification of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  These
spatially diffuse groups typically have velocity dispersions of
$\approx$1\kms, though they can be much higher due to both projection
effects and internal dynamics.  As an extreme example, in the Hyades
the velocities of stars in the tidal tails are expected to
span up to $\pm 40$\kms relative to the cluster center
\citep{jerabkova_800_2021}.  The stars in such diffuse regions can be
verified to be the same age as the core members ({\it i.e.}, coeval)
through analyses of color-absolute magnitude diagrams, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are many
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a more immediate
consequence is that we now know the ages of many more stars, including
previously known planet hosts.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, and is the subject of the upcoming
study by R.~Kerr and collaborators.  Our primary interest in the
region stems from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore the
population of stars that were observed, we select candidate Cep-Her
members through four steps, the first three being identical to those
described in Section~3 of \citet{Kerr2021}.  We briefly summarize them
here.

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric, defined
such that the group member with the smallest core distance has a
weight of 1, the group member with the greatest core distance has a
weight of 0, and weights for the other group members are log-normally
distributed between these two extremes.  In Figure~\ref{fig:XYZvtang},
we show 26{,}960 objects with weight exceeding 0.02 as gray points,
and overplot 7{,}560 objects with weights exceeding 0.10 as black
points.  {\bf TODO: FIXME these object numbers impose pretty weak
quality cuts and include junk at G>18...  use
get\_clean\_gaia\_photometric\_sources too, since they come in for the
CAMDs}.

The previously known $\delta$~Lyr\ cluster ($l,b=68^\circ,15^\circ$;
$v_{l'}, v_b=-4.5{\rm kms},-4{\rm kms}$) is visible, as is RSG-5
($l,b=83^\circ,6^\circ$, $v_{l'}, v_b=+5.5{\rm kms},-3.5{\rm kms}$).
Most of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
The fourth and final step was to cross-match our candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  This yielded 32 matches, of which 18
were known false positives, 7 were designated
``confirmed'', and 8 were designated ``candidates''.  A cursory
inspection of the Kepler data validation summaries and Robovetter
classifications for these objects quickly showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{\it
e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.

@@

Color-absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which are designed to
include binaries while omitting instrumental artifacts from for
instance low photometric signal to noise, or a small number of
visibility periods.  We then corrected for extinction using the
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}}
dust maps and the extinction coefficients $k_X\equiv A_X/A_0$from
\citet{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.  This
yielded a mean and standard deviation for the reddening of
$E(B-V)=0.036\pm0.002$ for RSG-5, and $E(B-V)=0.017\pm0.001$
for CH-2.  By way of comparison, in \citet{bouma_kep1627_2022} the
same query for the $\delta$~Lyr cluster yielded
$E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the $\bpmrpo$
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

>>>>

%
% Symbols
%
\newcommand{\kms}{\,km\,s$^{-1}$}
\newcommand{\mkms}{{\rm \,km\,s^{-1}}}  % math mode
\newcommand{\ms}{\,m\,s$^{-1}$}
\newcommand{\bpmrpo}{(G_{\rm BP}-G_{\rm RP})_0}
\newcommand{\bpmrp}{G_{\rm BP}-G_{\rm RP}}

@@

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar group memberships
\citep[{\it e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
To date these analyses have mostly clustered on the stellar positions and
on-sky velocities measured by Gaia, with varying degrees of filtering
and supervision.  One important result is the identification of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  These
spatially diffuse groups typically have velocity dispersions of
$\approx$1\kms, though they can be much higher due to both projection
effects and internal dynamics.  As an extreme example, in the Hyades
the velocities of stars in the tidal tails are thought to
span up to $\pm 40\mkms$ relative to the cluster center
\citep{jerabkova_800_2021}.  The stars in such diffuse regions can be
verified to be the same age as the core members ({\it i.e.}, coeval)
through analyses of color-absolute magnitude diagrams, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are many
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a more immediate
consequence is that we now know the ages of many more stars, including
previously known planet hosts.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, and will be the subject of the upcoming
study by R.~Kerr and collaborators.  Our primary interest in the
region stems from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore the
population of stars that were observed, we select candidate Cep-Her
members through four steps, the first three being identical to those
described in Section~3 of \citet{Kerr2021}.  We briefly summarize them
here.

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric, defined
such that the group member with the smallest core distance has a
weight of 1, the group member with the greatest core distance has a
weight of 0, and weights for the other group members are log-normally
distributed between these two extremes.  In Figure~\ref{fig:XYZvtang},
we show 12{,}436 objects with weight exceeding 0.02 as gray points,
and overplot 4{,}763 objects with weights exceeding 0.10 as black
points.\footnote{These counts only include objects with reliable astrometry
	and photometry: $\varpi/\sigma_\varpi>5$;
	$G/\sigma_{G}>50$;
	$G_{\rm RP}/\sigma_{G_{RP}}>20$;
	$G_{\rm BP}/\sigma_{G_{BP}}>20$.}
The previously known $\delta$~Lyr\ cluster ($l,b=68^\circ,15^\circ$;
$v_{l'}, v_b=-4.5 \mkms,-4 \mkms$) is visible, as is RSG-5
($l,b=83^\circ,6^\circ$; $v_{l'}, v_b=5.5 \mkms,-3.5 \mkms$).
Most of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
The fourth and final step was to cross-match our candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members
with weights exceeding 0.02, this yielded
 yielded 25 matches, of which 11
were known false positives, 6 were designated
``confirmed'', and 8 were designated ``candidates''.  
Inspection of the Kepler data validation summaries and Robovetter
classifications for these objects then showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{\it
e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.

@@

Color-absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which are designed to
include binaries while omitting instrumental artifacts from for
instance low photometric signal to noise, or a small number of
visibility periods.  We then corrected for extinction using the
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}}
dust maps and the extinction coefficients $k_X\equiv A_X/A_0$ from
\citet{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.  This
yielded a mean and standard deviation for the reddening of
$E(B-V)=0.036\pm0.002$ for RSG-5, and $E(B-V)=0.017\pm0.001$
for CH-2.  By way of comparison, in \citet{bouma_kep1627_2022} the
same query for the $\delta$~Lyr cluster yielded
$E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the $\bpmrpo$
color range to best visualize the region of maximal age information
content: the pre-main-sequence.
